Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-03 prop_iop.tex
prop_iop.tex \section{Mermin Square} Adding...
prop_iop.tex \section{Cryptodeterminism} Updating...

\noindent The answer is ``no'' due to the Kochen-Specker theorem.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\newpage{}%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}

>>>>

The answer is ``no'' due to the Kochen-Specker theorem whose proof
can also be formulated in the language of cryptodeterministic measure
as in \ref{sec:MerminSquare}.

@@

\section{Mermin Square\label{sec:MerminSquare}}

The Kochen-Specker theorem can be proved easily by considering a pair
of spin $\frac{1}{2}$ system with the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\[
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}
\]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
